--- 
title: "Evaluation and Aggregation of Covid-19 Death Forecasts in the United States"
author: "Nikos Bosse"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: 
  #thesisdown::thesis_pdf: default
  bookdown::pdf_book:
    fig_caption: yes
    toc_depth: 3
    latex_engine: pdflatex
documentclass: book
bibliography: [bib/masterthesis.bib, bib/packages.bib]
biblio-style: apalike
link-citations: yes
header-includes:
  - \usepackage{amssymb}
github-repo: nikosbosse/master_thesis
description: "This thesis, titled 'Evaluation and Aggregation of Covid-19 death forecasts in the United States' was submitted as a master thesis in Applied Statistics at the Universität Göttingen in September 2020."
---

```{r setup, include=FALSE}
library(kableExtra)
library(magrittr)
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(.packages(), 
                   'bookdown', 'knitr', 'rmarkdown', 'nloptr',
                   'scoringutils',
                   'EpiSoon', 'EpiNow', 'EpiNow2',
                   'stackr', 'forecastHybrid', 
                   'quantgen', 'rstan'), 
                 'bib/packages.bib')
```


# Todo

- Maybe add the different possible calibration types to the evaluation chapter

- Read more about stacking. Is the QRA stacking? 

- Do I want a summary section for each Chapter? 

- Maybe implement an equally weighted mixture ensemble

- consistent writing of Chapter / chapter

- Work through all the citations and adapt the author names in the bib file so they get shown consistently

- Use present tense or future tense consistently in the Chapter introduction paragraphs

- WIS in Chapter 3: PART THAT WIS FOR ALPHA = 0 IS PROPORTIONAL TO THE MAE

- Maybe add example plots to `scoringutils`

- Maybe add a part for Point Forecast Scores in Evaluation Chapter. The Part about when to use MAE and MSE. Also maybe add those to scoringutils

- Chapter 5 results: Report mean as well as Median for scores (in the plots)

- Make a plot with quantile deviation by range --> visualisation of bias. 

- Explain more how I got to the set of scores I summarise over, and how the ensemble models are formed

- Add a note that the regression framework was proposed by the Forecast Hub. 

